Trifunctional Sphingosine

### 2025-03-04 LipidProbe/Sphinganine.qmd
trying to distinguish cell types more effectively on individual probe pages
adding credit to Berit for the structures

---
title: "Trifunctional Sphinganine"
prefer-html: true
format: html
---

@@

:::{.border}
![Trifunctional Sphinganine](/LipidProbe/Structures/TF_Sphinganine.png)
:::

>>>>

---
title: "Trifunctional Sphinganine"
prefer-html: true
format: html
callout-icon: false
---

@@

:::{.border}
![Trifunctional Sphinganine. Chemical structure drawn by Berit Blume.](/LipidProbe/Structures/TF_Sphinganine.png)
:::

### 2025-03-04 LipidProbe/Sphingosine.qmd
trying to distinguish cell types more effectively on individual probe pages
adding credit to Berit for the structures

---
title: "Trifunctional Sphingosine"
format: html
prefer-html: true
---

@@

:::{.border}
![Trifunctional Sphingosine](/LipidProbe/Structures/TF_Sphingosine.png)
:::

@@

>>>>

---
title: "Trifunctional Sphingosine"
format: html
prefer-html: true
callout-icon: false
---

@@

:::{.border}
![Trifunctional Sphingosine. Chemical structure drawn by Berit Blume.](/LipidProbe/Structures/TF_Sphingosine.png)
:::

@@

::::

:::: {.callout-tip}
